Security on Networks

### 2013-05-14 paper/paper.tex
Working on karger's part.

Karger solves the all terminal problem using a reduction to D

>>>>

Karger solves the all terminal problem using a combination of a minimum cut finding algorithm and the Monte Carlo scheme. If $\tilde{P}_i$ is large, then it is sufficient to use the Monte Carlo algorithm because of the time bound of $O(\log n / (\epsilon^2 \tilde{P}))$. However, when $\tilde{P}$ is small and arbitrarily close to zero, the Monte Carlo simulation requires a prohibitive number of trials. Therefore, Karger develops another polynomial time algorithm which can be used when $\tilde{P} < 1/n^4$. When this is the case, we can find cuts that are small enough, and these cuts will provide an easy way to estimate the probability of failure.

To make this argument more rigorous, we shall develop the theory more formally. Notice that graphs become disconnected exactly when all the edges in a cut fail. Thus, it is clear that if each edge $i$ in a cut fails with probability $q_i$, then the cut will fail with probability $\prod_i q_i$. Karger proves the following useful lemma.

\begin{lemma}
  Suppose $c$ is the weight of the minimum cut and an $\alpha$-minimum cut is any cut with weight less than or equal to $\alpha c$, then there are at most $n^{\alpha c}$ $\alpha$-minimum cuts.
\end{lemma}

Karger (1999) also shows that when the probability of the minimum cut failing is small, then we only need to determine the probability that a cut of value close to $c$ fails. The paper proceeds to show that it is sufficient to find the all $\alpha$-minimum cuts, of which there are $O(n^{\alpha c})$ using Karger's Recursive Contraction Algorithm. This produces a set of near minimum cuts, from which we can then compute the loss probability
Now suppose that $c$ is the weight of the minimum cut. Karger proves the fo
